Modern Byte Pair Tokenizers are Zipfian

### 2025-05-14 writeup/paper.tex
kstests

The p-values for the Kolmogorov-Smirnov Tests for each considered distribution are summarized in Table \ref{tbl:pvals}.

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Distribution} & \textbf{bookscorpus} & \textbf{MiniPile} \\
        \hline
        Zipf &  &  \\
        \hline
        Exponential &  &  \\
        \hline
        log-normal &  &  \\
        \hline
    \end{tabular}
    \caption{RoBERTa (GPT-4) tokenizer's Kolmogorov-Smirnov test p-values}
    \label{tbl:pvals}
\end{table}

>>>>

The Kolmogorov-Smirnov test statistics for each considered distribution are summarized in Table \ref{tbl:kstest}.

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
        \textbf{Distribution} & \multicolumn{2}{c|}{\textbf{Words}} & \multicolumn{2}{c|}{\textbf{RoBERTa}} & \multicolumn{2}{c|}{\textbf{GPT-4}}  \\
        \hline
        Zipf &  &  &  &  &  &  \\
        \hline
        Exponential & 0.874 & 0.808 & 0.580 & 0.482 & 0.718 & 0.563 \\
        \hline
        log-normal & 0.379 & 0.451 & 0.032 & 0.050 & 0.397 & 0.283 \\
        \hline
    \end{tabular}
    \caption{Kolmogorov-Smirnov test statistics for distribution fit, where the left subcolumn is bookscorpus and the right subcolumn MiniPile}
    \label{tbl:kstest}
\end{table}
